\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
% \usepackage[absolute,noshowtext,showboxes]{textpos}
\usepackage{xeCJK}
\setCJKmainfont{WenQuanYi Zen Hei}
\usepackage{color}
\usepackage[absolute,showboxes]{textpos}
% \textblockorigin{-0.02cm}{0.07cm} %HPDeskJet5160
% \textblockorigin{0.00cm}{0.00cm} %HPDeskJet5160
\textblockorigin{0.00cm}{0.03cm} %HPDeskJet5160
\textblockorigin{0.05cm}{0.13cm} %HPDeskJet5160
% \textblockorigin{0.00cm}{0.00cm} %HPLaserJet5000LE
\usepackage{texdraw}
\pagestyle{empty}
\setlength{\unitlength}{1cm}

\newcommand{\myXdiazXZeroXIdentifier}[0]{
補習班 job
}

\newcommand{\myXdiazXZeroXAcontent}[0]{
Dr Bean's friend, Steve Hoover is looking for an \vspace{-0.4cm} \\ \begin{center} {\Large Assistant} \end{center}  to answer the phone, greet visitors and do some clerical work at his wife's 補息班 in 頭份. The pay is competitive, and the atmosphere is friendly. \par If you are interested email Steve at stephen.e.hoover@gmail.com, and include your phone number. He will call back, probably in the evening.
}

\newcommand{\myXdiazXZeroXBcontent}[0]{
Dr Bean's friend, Steve Hoover is looking for an assistant to answer the phone, greet visitors and do some clerical work at his wife's 補息班 in 頭份. The pay is competitive, and the atmosphere is friendly. If you are interested email Steve at stephen.e.hoover@gmail.com, and include your phone number. He will call back, probably in the evening.
}

\newcommand{\myXdiazXZeroXCcontent}[0]{
Dr Bean's friend, Steve Hoover is looking for an assistant to answer the phone, greet visitors and do some clerical work at his wife's 補息班 in 頭份. The pay is competitive, and the atmosphere is friendly. If you are interested email Steve at stephen.e.hoover@gmail.com, and include your phone number. He will call back, probably in the evening.
}

% \newcommand{\myDcontent}[0]{
% 
% }

\newcommand{\mycard}[5]{%
	\vspace{0.3cm}
	\tiny #1 #2
	\vspace{-0.2cm}
	\par
	\parbox[t][6.9cm][c]{10.5cm}{%
	\hspace{0.1cm} \large#3\\
	\normalsize#4 #5
	}
}

\begin{document}
\fontfamily{hlst}\fontseries{b}\fontshape{n}\selectfont
% \begin{picture}(15,20)(+4.8,-22.05)
% \begin{tabular}[t]{*{2}{|p{10.05cm}}|}

\begin{textblock}{8}(0,0)
\textblocklabel{picture1}
\mycard{}{\myXdiazXZeroXIdentifier}{\parbox{8.0cm}{A:
\myXdiazXZeroXAcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,0)
\textblocklabel{picture2}
\mycard{}{\myXdiazXZeroXIdentifier}{\parbox{9.0cm}{B:
\myXdiazXZeroXBcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,4)
\textblocklabel{picture3}
\mycard{}{\myXdiazXZeroXIdentifier}{\parbox{9.0cm}{C:
\myXdiazXZeroXCcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,4)
\textblocklabel{picture5}
\mycard{}{\myXdiazXZeroXIdentifier}{\parbox{9.0cm}{A:
\myXdiazXZeroXAcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,8)
\textblocklabel{picture5}
\mycard{}{\myXdiazXZeroXIdentifier}{\parbox{9.0cm}{A:
\myXdiazXZeroXAcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,8)
\textblocklabel{picture6}
\mycard{}{\myXdiazXZeroXIdentifier}{\parbox{9.0cm}{B:
\myXdiazXZeroXBcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(0,12)
\textblocklabel{picture7}
\mycard{}{\myXdiazXZeroXIdentifier}{\parbox{9.0cm}{C:
\myXdiazXZeroXCcontent
}}{}{} 
\end{textblock}

\begin{textblock}{8}(8,12)
\textblocklabel{picture5}
\mycard{}{\myXdiazXZeroXIdentifier}{\parbox{9.0cm}{A:
\myXdiazXZeroXAcontent
}}{}{} 
\end{textblock}

% \begin{textblock}{8}(8,4)
% \textblocklabel{picture7}
% \mycard{}{\myXdiazXZeroXIdentifier}{\parbox{9.0cm}{D:
% \myDcontent
% }}{}{} 
% \end{textblock}

\end{document}


